Making ice sheet models \\ scale properly

### 2023-01-02 talk/slides.tex
progress

@@

\section{what is an ice sheet model}

@@

@@

>>>>

\titlegraphic{\hfill \includegraphics[width=0.2\textwidth]{images/uafbw.png}}

@@

\section{what is an ice sheet model?}

@@

\begin{columns}
\begin{column}{0.63\textwidth}
\begin{itemize}
\item ice is modeled as a non-Newtonian viscous fluid at large scale
    \begin{itemize}
    \item[$\circ$] more on that later \dots
    \end{itemize}
\item ice sheets evolve their geometry and velocity \emph{in contact with climate}
    \begin{itemize}
    \item[$\circ$] snowfall
    \item[$\circ$] surface melt
    \item[$\circ$] subglacial melt
    \item[$\circ$] melt and calving of parts which float in ocean (\emph{ice shelves})
    \end{itemize}
\end{itemize}
\end{column}
\begin{column}{0.4\textwidth}
\includegraphics[width=\textwidth]{images/coverfig.png}
\end{column}
\end{columns}
\end{frame}

\begin{columns}
\begin{column}{0.63\textwidth}
\begin{itemize}
\item for purposes of clarity and analysis, let us simplify
\item inputs into an ice sheet model:
\item outputs from an ice sheet model:
\end{itemize}
\end{column}
\begin{column}{0.4\textwidth}
\includegraphics[width=\textwidth]{images/coverfig.png}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{z}

@@

\section{more on numerical stability}

\section{}
